%====================
% EXPERIENCE
%====================

\subsection{{AI Engineer – Network Intelligence \& AI Platforms \hfill Jul 2025 --- Present}}
\subtext{AWTG \hfill London, UK}
\begin{zitemize}

\item Led the end-to-end delivery of enterprise AI solutions, transforming proof-of-concept ideas into production-ready applications by combining \textbf{LLMs}, retrieval systems, workflow orchestration, secure APIs, and cloud-native deployment.

\item Scaled an AI-powered customer support platform for the \textbf{British Council} from an early proof of concept into a production solution supporting over \textbf{65,000 active users}. Designed the retrieval architecture, workflow orchestration, AI guardrails, and evaluation pipelines, enabling grounded responses while reducing manual customer support effort.

\item Collaborated on AI solutions supporting government border operations by developing conversational AI capabilities using LLMs, retrieval augmentation, workflow automation, and policy-aware decision support while ensuring governance, compliance, explainability, auditability, and end-to-end traceability throughout the decision-making process.

\item Solved inconsistent AI responses across enterprise knowledge bases by designing \textbf{Hybrid RAG} and \textbf{GraphRAG} architectures using knowledge graphs, vector search, metadata enrichment, and semantic retrieval, improving multi-hop reasoning, contextual retrieval, explainability, and evidence-backed answer generation.

\item Established enterprise AI governance by implementing AI guardrails, policy enforcement, prompt versioning, access controls, audit logging, traceability, and human-in-the-loop workflows, enabling secure, compliant, explainable, and production-ready AI systems.

\item Built AI observability and evaluation frameworks that continuously monitored groundedness, hallucination rates, retrieval quality, latency, safety, operational cost, and user feedback while providing complete traceability between user prompts, retrieved evidence, tool execution, and generated responses.

\item Co-designed and developed \href{https://platform.awtg.ai/login}{\textbf{KAI}}, an enterprise AI platform providing reusable agent orchestration, secure tool execution, memory management, retrieval services, workflow automation, and enterprise integrations, significantly accelerating AI solution delivery across multiple customer engagements.

\item Developed production-ready AI applications using \textbf{GPT}, \textbf{Claude}, \textbf{Llama}, and \textbf{Mistral}, integrating context engineering, structured outputs, tool calling, enterprise knowledge retrieval, and backend services to improve decision support and operational efficiency.

\item Successfully designed and evaluated an intelligent handover optimisation framework between \textbf{Terrestrial Networks (TN)} and \textbf{Non-Terrestrial Networks (NTN)} using \textbf{Reinforcement Learning}, deep learning, and Generative AI. Modelled network selection using mobility, radio, latency, throughput, and service continuity to optimise adaptive handover decisions beyond traditional rule-based approaches.

\item Integrated AI services with \textbf{HubSpot}, \textbf{Salesforce}, and enterprise APIs to automate CRM synchronisation, lead qualification, customer engagement workflows, and email-triggered actions while maintaining secure authentication, governance, and auditability.

\item Applied modern software engineering practices including \textbf{Python}, Git, Docker, CI/CD, Azure Container Apps, Azure Functions, and automated testing to deliver scalable, secure, and production-ready AI systems while mentoring engineers on GraphRAG, enterprise retrieval, AI evaluation, governance, and production deployment.

\end{zitemize}


%====================
% EXPERIENCE
%====================

\subsection{{Senior AI/ML Engineer \hfill May 2020 --- Sept 2024}}
\subtext{Accenture \hfill Pune, India}
\begin{zitemize}

\item Delivered end-to-end AI and machine learning solutions for enterprise clients, translating complex business problems into scalable production systems supporting forecasting, optimisation, conversational intelligence, and decision support.

\item Built conversational AI and enterprise knowledge assistants using \textbf{LangChain}, Hugging Face Transformers, retrieval-based architectures, and Python, improving response quality and enabling natural-language access to enterprise information.

\item Designed scalable data pipelines for ingestion, validation, transformation, and feature engineering across structured and unstructured datasets, improving data quality and reducing manual processing effort.

\item Developed machine learning solutions for forecasting, anomaly detection, optimisation, predictive analytics, and business intelligence, enabling data-driven operational and strategic decision-making.

\item Implemented automated model evaluation, regression testing, quality assurance, and monitoring pipelines that improved deployment confidence and reduced production defects.

\item Built reusable backend APIs and inference services that integrated machine learning models into enterprise applications and operational workflows.

\item Partnered with product owners, business analysts, and technical stakeholders to define success metrics, prioritise delivery roadmaps, and communicate AI solutions to both technical and executive audiences.

\item Applied software engineering best practices including Git, automated testing, documentation, and CI/CD pipelines to deliver maintainable, scalable, and production-ready AI applications.

\end{zitemize}


%====================
% EXPERIENCE
%====================

\subsection{{Reporting Analyst \hfill Jul 2019 --- May 2020}}
\subtext{EXL Services \hfill Bangalore, India}
\begin{zitemize}

\item Built scalable data pipelines using \textbf{Python} and \textbf{PySpark}, consolidating fragmented reporting systems and improving data reliability for enterprise analytics and downstream AI use cases.

\item Automated reporting, validation, reconciliation, and data quality workflows, reducing manual effort while improving reporting accuracy and operational efficiency.

\item Engineered analytical datasets through feature engineering, anomaly detection, and data quality assurance, improving readiness for predictive analytics and machine learning initiatives.

\item Collaborated with business stakeholders to translate reporting requirements into scalable analytical solutions, enabling faster operational reporting and data-driven decision-making.

\end{zitemize}